|

### 2025-07-24 output/IMPS-2025-slideshow.qmd
Final notes tweaked
Clarify that the "transorm matrix" is an example

@@

As you see here, the latent space Gram matrix is the inverse covariance matrix (which results from the transformation matrix P, pre-multiplied by itself, P\^T P).
The invariant distance then, in the latent space, is the Mahalanobis distance, which is the square root of the inner product of the latent trait vector with itself.
And in the test space, the Gram matrix is the covariance distance.

@@

::: notes
The complete definition and representation of the parameters is as you see here.

@@

<center>Contact: [danielmorillo.ac\@gmail.com](mailto:danielmorillo.ac@gmail.com){.email}</center>

>>>>

::: {.fragment fragment-index="1"}
$$
  \text{example:} \qquad
  \mathbf{\Sigma} = \begin{bmatrix}
      1 & 0.5 \\
      0.5 & 1
    \end{bmatrix}
$$
:::

@@

As you see here, the latent space Gram matrix is the inverse covariance matrix (which results from the transformation matrix P, pre-multiplied by itself, P\^T P).
The invariant distance then, in the latent space, is the Mahalanobis distance, which is the square root of the inner product of the latent trait vector with itself.

And in the test space, the Gram matrix is the covariance matrix.

@@

::: notes
The complete definition of the parameters is as you see here.

@@

Contact: [danielmorillo.ac\@gmail.com](mailto:danielmorillo.ac@gmail.com){.email}

Comments & questions welcome!

Read the preprint: <https://bit.ly/mirt-preprint>
